VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-19 snapshot_system/paper_eval.tex
revise
wording

Comparing the experiment results of the sampled index method reported in~\cite{Guo2011}, 
our scheme achieves a 85K:1 ratio between raw snapshot data and memory usage 
with 96\% deduplication efficiency
while the sampled index method achieves 20K:1 (25GB memory per 500TB raw data)
with 97\% deduplication efficiency.
Thus our scheme is more memory efficient with a good tradeoff for deduplication efficiency.
If we change $\sigma=4\%$, the deduplication efficiency of VC increases to 96.58\% while
memory usage per machine increases to about 220MB. 
Notice that the sampled index method is designed for single-machine deduplication.
%and it is not easy to extend to a distributed cluster architecture.

@@

 Table~\ref{tab:vm-availability} shows 
that VC has a significantly  higher availability than VO.
% as the number of failed machines increases from 3 to 20.
%Our VM-centric approach shows significant improvements
%in VM availability.
With $p=100$ and 3 failures,
VO with 69.5\% availability could lose data in 763 VMs 
while VC with 99.7\% only loses data for 8 VMs out of 2500 VMs.
The key reason is that for most data in VC, only a single VM can be affected by
the loss of a single file block
%Since most blocks contain chunks for a single
%VM, VMs can depend on a smaller number of blocks, 
while in VO, the loss of a
single block tends to affect many VMs.
When the number of physical machines failed reaches 20, the availability of VO reaches 0\%
and VC also drops to 1.13\%. This is because even there is a good availability for PDS data, VC still
loses most of non-PDS blocks given the replication degree for non PDS is 3.
When $p=1000$, the percentage of failures is then 2\% and VC delivers a meaningful availability 
with 99.62\%, outperforming VO significantly.

>>>>

Comparing the experiment results of the sampled index method reported in~\cite{Guo2011}, 
our scheme achieves a 85K:1 ratio between raw snapshot data and memory usage 
with 96\% deduplication efficiency
while the sampled index method achieves 20K:1 (25GB memory per 500TB raw data)
with 97\% deduplication efficiency.
Thus our scheme is more memory efficient with a good tradeoff for deduplication efficiency.
If we change $\sigma=4\%$, the deduplication efficiency of VC increases to 96.58\% while
memory usage per machine increases to about 220MB. 
Notice also that the sampled index method is designed for single-machine deduplication.
%and it is not easy to extend to a distributed cluster architecture.

@@

 Table~\ref{tab:vm-availability} shows 
that VC has a significantly  higher availability than VO.
% as the number of failed machines increases from 3 to 20.
%Our VM-centric approach shows significant improvements
%in VM availability.
With $p=100$ and 3 failures,
VO with 69.5\% availability could lose data in 763 VMs 
while VC with 99.7\% only loses data for 8 VMs out of 2500 VMs.
The key reason is that for most data in VC, only a single VM can be affected by
the loss of a single file block
%Since most blocks contain chunks for a single
%VM, VMs can depend on a smaller number of blocks, 
while in VO, the loss of a
single block tends to affect many VMs.
When the number of physical machines failed reaches 20, the availability of VO reaches 0\%
and VC also drops to 1.13\%. This is because even though availability for PDS data remains good, VC still
loses many of the non-PDS blocks given the replication degree for non-PDS is 3.
When $p=1000$, the percentage of failures is then 2\% and VC delivers a meaningful availability 
with 99.62\%, outperforming VO significantly.
